Proof nets for first-order additive linear logic

### 2018-01-22 ALL1.tex
accept suggestion

\author[1]{Willem B.\ Heijltjes}
\author[2]{Dominic J.D.\ Hughes}
\author[3]{Lutz Stra\ss burger}
\affil[1]{University of Bath, United Kingdom\\
  \url{http://www.cs.bath.ac.uk/~wbh22/}} %%\texttt{w.b.heijltjes@bath.ac.uk}}
\affil[2]{Logic Group, UC Berkeley, USA\\
  \url{http://boole.stanford.edu/~dominic/}} %%\texttt{dominich@theory.stanford.edu}}
\affil[3]{Inria Saclay \&\ LIX/\'Ecole Polytechnique, Palaiseau, France\\
  \url{http://www.lix.polytechnique.fr/Labo/Lutz.Strassburger/}} %%\texttt{lutz.strassburger@inria.fr}}
\authorrunning{W.B.\ Heijltjes, D.J.D.\ Hughes, and L.\ Stra\ss burger}

@@

\begin{definition}
A witness pre-net $\net{\lambda_\Sigma}AB$ has \defn{exact coverage} if for every link $\link CD$ in $\lambda_\Sigma$ the domain of $\sigma$ is exactly the existential variables of $C$ and $D$:
\[
	\dom\sigma = \ex[A]C\cup\ex[B]D~.
\]
\end{definition}
%
% ..................................................
%
The witness map $\sigma$ of a link $\link CD$ then has two natural \lutz{disjoint?} components, $\sigma\res{\ex[A]C}$ and $\sigma\res{\ex[B]D}$, which we will abbreviate by $\sigma_C$ and $\sigma_D$ respectively.

>>>>

\author[1]{Willem B.\ Heijltjes}
\author[2]{Dominic J.D.\ Hughes}
\author[3]{Lutz Stra\ss burger}
\affil[1]{University of Bath, United Kingdom\\
  \url{http://willem.heijltj.es/}} %%\texttt{w.b.heijltjes@bath.ac.uk}}
\affil[2]{Logic Group, UC Berkeley, USA\\
  \url{http://boole.stanford.edu/~dominic/}} %%\texttt{dominich@theory.stanford.edu}}
\affil[3]{Inria Saclay \&\ LIX/\'Ecole Polytechnique, Palaiseau, France\\
  \url{http://www.lix.polytechnique.fr/Labo/Lutz.Strassburger/}} %%\texttt{lutz.strassburger@inria.fr}}
\authorrunning{W.B.\ Heijltjes, D.J.D.\ Hughes, and L.\ Stra\ss burger}

@@

\begin{definition}
A witness pre-net $\net{\lambda_\Sigma}AB$ has \defn{exact coverage} if for every link $\link CD$ in $\lambda_\Sigma$ the domain of $\sigma$ is exactly the existential variables of $C$ and $D$:
\[
	\dom\sigma = \ex[A]C\cup\ex[B]D~.
\]
\end{definition}
%
% ..................................................
%
The witness map $\sigma$ of a link $\link CD$ then has two natural, disjoint components, $\sigma\res{\ex[A]C}$ and $\sigma\res{\ex[B]D}$, which we will abbreviate by $\sigma_C$ and $\sigma_D$ respectively.
